Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-17 paper.tex
reviewed section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Those nine challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where controlled objects ({\it e.g.}, physical plants) typically exhibit continuous behavior (which may eventually change), whereas controllers (usually implemented by real-time computer systems) operate in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for embedded systems.

@@

This position paper tackles seven major problems in computer-aided verification and synthesis for ECPS, which are (partially) open in current published research.

@@

\textbf{(RP2)} exploitation of SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

>>>>

Those nine challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where controlled objects ({\it e.g.}, physical plants) typically exhibit continuous behavior (which may eventually change), whereas controllers (usually implemented by real-time computer systems) operate in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of quantizers (A/D and D/A converters), when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered, when correct-by-construction code is generated for ECPS.

@@

This survey tackles seven major problems in computer-aided verification and synthesis for ECPS, which are (partially) open in current published research.

@@

\textbf{(RP2)} exploitation of SMT techniques to leverage (bounded) model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.
